### 2021-06-05 paper/report.tex
Another paragraph, shuffled figures around a little bit.

        \includegraphics[width=\textwidth]{../figures/model-graph-bottom-left}
        \caption{{\small PCR and antigen tests}}
        \label{fig:pcr_antigen_tests}
    \end{subfigure}
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

@@

We apply this model to Germany. In March and April 2020, the country broke the first wave of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We start our analysis in mid-September for two reasons. First, we do not include the first wave because the environment was very different (e.g., aggregate PCR test capacity was much lower and we would require a very different model for calculating the share of known cases) and some data was not recorded yet.\comment[id=HM]{True?}. Many cases during the summer of 2020 were traced to international travellers; our model is not very helpful in explaining this.

In late summer and early fall, restrictions were few. A distance of 1.5m had to be kept and masking requirements were enforced in public locations.\comment[id=HM]{pls double-check, add if I am missing important stuff}. Figure~\ref{fig:pandemic_drivers_model_fit} describes the background for our analysis. Figure~\ref{fig:stringency_index} Important to remember that multipliers are relative to that period

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/work_multiplier_since_sep}
        Stringency index + multipliers

@@

        \caption{{\small Contact reductions}}
        \label{fig:stringency_index}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

@@

        \caption{{\small Tests and vaccinations}}
        \label{fig:pcr_antigen_tests_vaccinations}
    \end{subfigure}
    \vskip3ex

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/share_of_b117_acc_to_rki}

@@

        \caption{Share of known cases and fraction of B.1.1.7 strain}
        \label{fig:share_known_cases_b117}
    \end{subfigure}
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case}
        \caption{{\small Recorded cases: Empirical and simulated}}
        \label{fig:aggregated_fit}
    \end{subfigure}

    \caption{Drivers of the pandemic and model fit, September 2020 to May 2021}
    \label{fig:pandemic_drivers_model_fit}

@@

        \caption{Decomposition of effects for Figure~\ref{fig:full_newly_infected_cropped}}
        \label{fig:decompisition total cases}
    \end{subfigure}
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

>>>>

        \includegraphics[width=\textwidth]{../figures/model-graph-bottom-left}
        \caption{{\small PCR and antigen tests}}
        \label{fig:pcr_antigen_tests}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

@@

We apply this model to Germany. In March and April 2020, the country broke the first wave of the pandemic fairly quickly. Between mid-May and mid-September, daily new infections were below 20 per Million and day.\comment[id=HM]{Cite our world in data} We start our analysis in mid-September for two reasons. First, we do not include the first wave because the environment was very different (e.g., aggregate PCR test capacity was much lower and we would require a very different model for calculating the share of known cases) and some data was not recorded yet.\comment[id=HM]{True?}. Second, a large fraction cases during summer of 2020 were traced to international travel,\comment[id=HM]{citation?} which is not part of this model.

We describe the evolution of the pandemic and of its drivers in Figure~\ref{fig:pandemic_drivers_model_fit}. The black line in Figure~\ref{fig:aggregated_fit} shows the officially recorded cases; the \replace[id=HM]{color} line in

The setting in our analysis 
In late summer and early fall, restrictions were few. A distance of 1.5m had to be kept and masking requirements were enforced in public locations.\comment[id=HM]{pls double-check, add if I am missing important stuff}. 
 Figure~\ref{fig:stringency_index} Important to remember that multipliers are relative to that period

@@

        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/combined_fit/full_new_known_case}
        \caption{{\small Recorded cases: Empirical and simulated}}
        \label{fig:aggregated_fit}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/work_multiplier_since_sep}
        Stringency index + multipliers

@@

        \caption{{\small Contact reductions}}
        \label{fig:stringency_index}
    \end{subfigure}

@@

        \caption{{\small Tests and vaccinations}}
        \label{fig:pcr_antigen_tests_vaccinations}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/data/share_of_b117_acc_to_rki}

@@

        \caption{Share of known cases and fraction of B.1.1.7 strain}
        \label{fig:share_known_cases_b117}
    \end{subfigure}

    \caption{Evolution of the pandemic, its drivers, and model fit, September 2020 to May 2021}
    \label{fig:pandemic_drivers_model_fit}

@@

        \caption{Decomposition of effects for Figure~\ref{fig:full_newly_infected_cropped}}
        \label{fig:decompisition total cases}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
